Women highest Level Education in 20 years

### 2023-03-12 outputs/paper/paper.qmd
add graphs to paper

## kind of an ugly graph buuuut yea ##

merged_gss |> group_by(Year) |> count(Highest_Educ_Level) |>
  ggplot(aes(x = Year, y = n, color = Highest_Educ_Level)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Year 2000"
  )

@@

## kind of an ugly graph buuuut yea ##

>>>>

## mean education level over 20 yrs ##

merged_gss |> group_by(Year) |> summarize(mean= mean(Highest_Educ_Level, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Mean highest education level of Women over 20 Years",
    x = "Year",
    y = "Mean Educ Level %"
  )

@@

## mean occ. prestige pct over 20 years ##
